---
title: "Answers of Pet Exercise"
author: "Mansun Kuo"
date: "May 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Here is a data.table contains four pets' name, species and weight:  

```{r}
library(data.table)
pets = data.table(name = c("Senor", "Cookie", "Lucky", "Meow Meow"),
                  species = c("dog", "dog", "bird", "cat"),
                  weight = c(26, 13, 0.5, 6))
```

Please:

1. Create a vector called **pet_weight** contains all pets' weight

```{r}
pet_weight = pets$weight
pet_weight
```


2. Create a unit vector **senor_weight** contains Senor's weight

```{r}
senor_weight = pets[name == "Senor", weight]
senor_weight
```


3. Create a data.table called **dogs_weight** that contains *name* and *weight* of all dogs in pets

```{r}
dogs_weight = pets[species == "dog", .(name, weight)]
dogs_weight
```


4. Modify Cookie's weight as 15

```{r}
pets[name == "Cookie", weight := 15]
pets
```


5. Create a data.table called **pet\_stat** that contains species, avg\_weight and count

```{r}
pet_stat = pets[, .(avg_weight = mean(weight), count = .N), by = "species"]
pet_stat
```

